Presentation Title

### 2017-06-26 thesis/chapters/ch1-intro.tex
Write problem description

Bitcoin has had its ups and downs, but over it has grown into an enormous system.
Its power consumption is as high as Republic of Ireland~\cite{o2014bitcoin}.
Its market cap, at the time of writing, is over 40 Trillion USD~\cite{bitcoinmarketcap}.
Many online marketplaces are using Bitcoin, for example Steam\footnote{\url{https://store.steampowered.com/}} and even Amazon\footnote{Not directly, but via \url{https://purse.io/}.}.
Due to its success, people from many different disciplines began investigating in way to use blockchain technology.
This includes finance~\cite{todo}, heath care~\cite{todo}, logistics~\cite{todo}, energy~\cite{todo} and so on.

Sadly, as traditional blockchain systems began to gain popularity,
their limitations also became apparent.
Bitcoin has the infamous 7 transactions per second upper bound.
This is due to the fact that blocks are fixed to 1 MB are only generated on average every 10 minutes.
Since every Bitcoin transaction is at least 250 bytes, it computes to about 7 transactions per second.
Due to this limitation, it is not uncommon to see a long backlog of about 20000 transactions on \url{https://blockchain.info}\footnote{\url{https://blockchain.info/unconfirmed-transactions/}}.
A few months ago the backlog even reached 100000, which meant new transactions would take at least 11 hours to hit the blockchain~\cite{bitcoinbacklog}.
The issue has plagued the Bitcoin community for some time and is the root cause for the block size debate, which some calls it a civil war~\cite{bitcoincivilwar}.
Parties that are for the increase in block size argue that a larger block would improve the transaction rate.
Parties against it argue that it would make mining more centralised because blocks take longer to propogate through the network and it does not solve the fundamental problem.
A recent empirical study Croman et el.~\cite{croman2016scaling} has shown that simply increasing the block size may help.
But given the bandwidth and latency constraints, it not possible to have more than 758 transactions per second and it may give some miner an unfair lead over others.
Thus fundamental changes are necessary run at the scale of centralised payment processors such as Visa~\cite{visa}, which is in the order of tens of thousands transactions per second.

@@

>>>>

Bitcoin has had its ups and downs, but over it has grown into an enormous system.
Its power consumption is as high as Republic of Ireland~\cite{o2014bitcoin}.
Its market cap, at the time of writing, is over 40 billion USD~\cite{bitcoinmarketcap}.
Many online marketplaces are using Bitcoin, for example Steam\footnote{\url{https://store.steampowered.com/}} and even Amazon\footnote{Not directly, but via \url{https://purse.io/}.}.
Due to its success, people from many different disciplines began investigating in way to use blockchain technology.
This includes finance~\cite{todo}, heath care~\cite{todo}, logistics~\cite{todo}, energy~\cite{todo} and so on.

Sadly, as traditional blockchain systems began to gain popularity,
their limitations also became apparent.
Bitcoin has the infamous 7 transactions per second upper bound.
This is due to the fact that blocks are fixed to 1 MB are only generated on average every 10 minutes.
Since every Bitcoin transaction is at least 250 bytes, it computes to about 7 transactions per second.
Due to this limitation, it is not uncommon to see a long backlog of about 20000 transactions\footnote{\url{https://blockchain.info/unconfirmed-transactions/}}.
A few months ago the backlog even reached 100000, which meant new transactions would take at least 11 hours to hit the blockchain~\cite{bitcoinbacklog}.
The issue has plagued the Bitcoin community for some time and is the root cause for the block size debate, which some calls it a civil war~\cite{bitcoincivilwar}.
Parties that are for the increase in block size argue that a larger block would improve the transaction rate.
Parties against it argue that it would make mining more centralised because blocks take longer to propogate through the network.
It also requires a hard fork (not backward compatible), which risks consensus failure and devaluation.
A recent empirical study Croman et el.~\cite{croman2016scaling} has shown that increasing the block size may help.
But given the bandwidth and latency constraints,
it not possible to have more than 758 transactions per second.
Even worse, it may give some miner an unfair lead over others.
Thus fundamental changes are necessary run at the scale of centralised payment processors such as Visa~\cite{visa},
which is in the order of tens of thousands transactions per second.

What we have described is in fact the current state of Bitcoin.
Many proposals exist with the aim to make Bitcoin more scalable.
The most prominant is Seggregated Witness or SegWit~\cite{segwit}.
It moves the signature data to the end of the block and changes the block size to 4 MB.
The effect is that the first 1 MB of the block is still backward compatible, thus there is no need for a hard fork.
It also solves the transaction malleability problem~\cite{bitcoinmalleability} and paves the way for offchain transactions via Lightning Network~\cite{lightningnetwork}.
Although SegWit is implemented, it is still uncertain whether the Bitcoin network will adopt it.
At the time of writing, there is only 35\% of the network signalling for adoptation,
this is only a 10\% increase since November last year\footnote{\url{https://blockchain.info/charts/bip-9-segwit}}.
Thus it may take years if ever for SegWit to be adopted.
Even if it is adopted, it cannot reach the transaction rate of centralised systems.

@@

Using the aforementioned insight,
we explore an alternative consensus model for blockchain systems where transactions themself do not reach consensus,
but nevertheless verifiable at a later stage by any node in the network.
Informally, out model works as follows.
Every node stores its own blockchain and every block is one transaction.
We randomly selected nodes in every round, the selected ones are called facilitators.
They reach consensus not on the individual transactions,
but on the state of every chain represented by a single digest, we call this state the checkpoint.
If a checkpoint of some node is in consensus, 
then that node can proof to any other node that it holds a set of transactions that computes (form a chain) to the checkpoint.
This immediately show that those transactions are tamper-proof.

### 2017-06-26 thesis/chapters/ch2-problem.tex
Write problem description

- long history of BFT, since Lamport
- PBFT
- PBFT triggered a renaissance in BFT replication research, with protocols like Q/U

- classical blockchains are nice, but is it possible to also use 30 years of BFT research?
- non-consensus chains scales, but no consensus...
- alternative consensus model

@@

% Using the aforementioned insight,
% we explore an alternative consensus model for blockchain systems where transactions themself do not reach consensus,
% but nevertheless verifiable at a later stage by any node in the network.
% Informally, out model works as follows.
% Every node stores its own blockchain and every block is one transaction, same as the TrustChain construction.
% We randomly selected nodes in every round, the selected ones are called facilitators.
% They reach consensus not on the individual transactions,
% but on the state of every chain represented by a single digest, we call this state the checkpoint.
% If a checkpoint of some node is in consensus, 
% then that node can proof to any other node that it holds a set of transactions that computes (form a chain) to the checkpoint.
% This immediately show that those transactions are tamper-proof.

>>>>

Blockchain technology has many advantages over centralised systems.
Its decentralised and democratic nature removes central point of control or failure.
However, as we described in the Introduction, it faces a genuine scalability problem.
In particular, proof-of-work based systems are unlikely to reach the transaction rate of Visa even with parameter tuning.
What we wish to see is horizontal scalability.
That is, by adding new nodes into the network, the global transaction rate should increase proportionally.
Hence, the research question we answer in this  work is the following.
\begin{displayquote}
\emph{Is it possible to design a blockchain fabric that is fault tolerant, scalable and can reach global consensus?}
\end{displayquote}

In order to make sense of our research question, we must first define \emph{blockchain fabric}.
Typical blockchain systems are application specific.
For example, the application in Bitcoin (any many others) is digital cash, the application in Namecoin is domain name registration~\cite{namecoin} and the application in Siacoin is cloud storage~\cite{siacoin}.
Underneath these applications lies the blockchain fabric, which we call the consensus protocol, and it is abstract over the application.
In the case of Bitcoin it is proof-of-work (PoW) because PoW is not concerned with the structure of the transactions,
it works by simply treating transactions as a blob of data and hashes them with the previous block.
Hence, we wish to design an application neutral system.
It should act as a backbone that provides the building blocks of any blockchain based applications.
Also, it should be possible to build any kind of application on top our system.
We do not impose on a consensus algorithm, as long as it satisfies the properties of atomic broadcast which we describe in~\Cref{sec:overview-cons}.

In the remainder of this chapter we expand on our research question and visit each of our requirement in detail and discuss our approach.

\section{Global Consensus}

The first objective is to reach consensus on a global \emph{state}.
We emphasise the word state because in contrary to traditional blockchains,
it does not neccessarily mean the set of all transactions that has ever happened.
The state can be a verifiable representation of all the transactions.
As an extreme example, a single digest of the complete history can represent the state.
It is even verifiable as long as there are nodes that stores the history.

Traditional blockchain systems use PoW as the consensus algorithm.
However, consensus algorithm and especially Byzantine\footnote{Byzantine means participants can experience arbitrary failure, more on this in~\Cref{sec:acs-background}.}
consensus algorithms have existece since 1982,
where it is first introduced by Lamport et el.~\cite{lamport1982byzantine}.
The Practical Byzantine Fault Tolerance (PBFT) algorithm introduced in 1999 by Castro and Liskov~\cite{castro1999practical} is widely regarded as the first high-performance consensus algorithm.
Since then research in this area picked up pace and many more algorithms are introduced~\cite{abd2005fault, kotla2007zyzzyva}.
With the introduction of Bitcoin's probabilistic consensus model, the field experienced a second renaissance.
These include proof-of-stake protocols~\cite{bentov2016snow, micali2016algorand}, as well as protocols optimised for blockchain~\cite{liu2016xft, miller2016honey}.

Our approach is to combine the vast literature in Byzantine fault tolerance research with blockchain technology,
and introduce a new consensus model to record the global state.

\section{Security and Fault Tolerance}

The second objective is fault tolerance,
where our system should be unaffected in the presence of powerful adversaries.
In particular, adversaries are Byzantine meaning that they can have arbitrary behaviour.
Thus anything is possible from simply ommitting messages to colluding with eachother in order to undermine the whole system.
This asppect usually comes for free when using a Byzantine fault tolerant consensus algorithm.

There is another aspect of fault tolerance that is transaction verifiability.
Recall that it is not neccessary to reach consensus on all the transactions in order to record the state.
But when using some digest (or a set of digets) to represent the state, it is also important for the transactions to be verifiable.
Otherwise adversaries could simply store invalid transactions in the state and they would never be detected.

\section{Performance and Scalability}

The last but not least, the final objective is horizontal scalability.
We wish to see the performance (global transaction rate) increase as more nodes join the network.
BitTorrent~\cite{cohen2003incentives} is an example of such a system,
where peers interact with eachother to exchange files without any global bottleneck.

Traditional blockchain systems may run in a network of thousands of nodes, but the performance do not scale.
On the other hand, as we will see in~\Cref{sec:acs-background}, Byzantine consensus algorithms performs well but only when in a small network.
In this work we combine the ideas from both of these systems to create the first horizontally scalable blockchain fabric.

\section{Non-goals}
Due to the nature of our system, we do not explicitly address the Sybil attack~\cite{douceur2002sybil}.
Sybil defence mechanism always require some form of reputation score from the application.
For example, social network based Sybil defence mechanims use graph structure of real-world relationships~\cite{yu2006sybilguard}.
Online marketplaces such as Amazon use the rating of buyer and sellers.
Thus it is not possible to design a Sybil defence mechanism with a application neutral framework.
On the other hand, our system also has no restrictions on the Sybil defence technique
and applications built on top of our system can use the best mechanism for their purpose.

@@

### 2017-06-26 thesis/chapters/ch3-model.tex
New intro and etc.
Write problem description

The goals guiding our system design are as follows.
\begin{itemize}
    \item Performance and scalability,
    \item application neutrality and
    \item security.
\end{itemize}

As mentioned in the Introduction, the primary goal is performance and scalability.
Having a scalable blockchain system while still keeping global consensus
allows the system to be ubiquitous and realise the full potential of blockchain.

The secondary goal is to design an application neutral system.
In particular, it should act as a backbone that provides the building blocks of blockchain based applications.
It should be possible to buld any kind of application on top our system.
Further, we do not impose on a consensus algorithm, as long as it satisfies the properties of atomic broadcast which we describe in~\Cref{sec:overview-cons}.

Due to the nature of our system, we do not explicitly address the Sybil attack~\cite{douceur2002sybil}.
Sybil defence mechanism always require some form of reputation score from the application.
For example, social network based Sybil defence mechanims use graph structure of real-world relationships~\cite{yu2006sybilguard}.
Online marketplaces such as Amazon use the rating of buyer and sellers.
Thus it is not possible to design a Sybil defence mechanism with a application neutral framework.
On the other hand, our system also has no restrictions on the Sybil defence technique
and applications built on top of our system can use the best mechanism for their purpose.

The third and final goal is security.
Our system should be unaffected in the presence of powerful adversaries.
In particular, adversaries are Byzantine meaning that they can have arbitrary behaviour.
Thus anything is possible from simply ommitting messages to colluding with eachother in order to undermine the whole system.

We begin the chapter with an intuitive overview of the architecture in \Cref{sec:system-overview}.
Next, we give the formal description, starting with the model and assumptions in \Cref{sec:model-assumptions}.
Then, the three protocols which make up the complete system,
namely consensus protocol (\Cref{sec:cons-protocol}), transaction protocol (\Cref{sec:tx-protocol}) and validation protocol (\Cref{sec:vd-protocol}).
Finally, the possible extensions are described in \Cref{sec:protocol-extensions}.

@@

This section and the ones following it give a technical treatment of what the content in System Overview.
For notational clarity, we use the following convention (adapted from~\cite{miller2016honey}) throughout this work.
\begin{itemize}
\item Lower case (e.g. $x$) denotes a scalar object or a tuple.
\item Upper case (e.g. $X$) denotes a set or a constant.
\item Sans serif (e.g. $\textsf{fn}(\cdot)$) denotes a function.
\item Typewrite (e.g. $\texttt{ack}$) denotes message type.
\end{itemize}
Further, we use $a || b$ to denote concatination of the binary representations of $a$ and $b$.

>>>>

% As was shown in~\Cref{ch:problem}, the requirements are the following.
% \begin{itemize}
%     \item Global consensus
%     \item Security and fault tolerance
%     \item Performance and scalability
% \end{itemize}

% As mentioned in the Introduction, the primary goal is performance and scalability.
% Having a scalable blockchain system while still keeping global consensus
% allows the system to be ubiquitous and realise the full potential of blockchain.

% The secondary goal is to design an application neutral system.
% In particular, it should act as a backbone that provides the building blocks of blockchain based applications.
% It should be possible to buld any kind of application on top our system.
% Further, we do not impose on a consensus algorithm, as long as it satisfies the properties of atomic broadcast which we describe in~\Cref{sec:overview-cons}.

% The third and final goal is security.
% Our system should be unaffected in the presence of powerful adversaries.
% In particular, adversaries are Byzantine meaning that they can have arbitrary behaviour.
% Thus anything is possible from simply ommitting messages to colluding with eachother in order to undermine the whole system.

The goal of this chapter is to detail our system specification.
We begin our discussion with an intuitive overview of the architecture in \Cref{sec:system-overview}.
Next, we give the formal description, starting with the model and assumptions in \Cref{sec:model-assumptions}.
Then, the three protocols which make up the complete system,
namely consensus protocol (\Cref{sec:cons-protocol}), transaction protocol (\Cref{sec:tx-protocol}) and validation protocol (\Cref{sec:vd-protocol}).
Finally, some optimisations are described in \Cref{sec:optimisations}.

@@

This section and the ones following it give a technical treatment of what the content in System Overview.
For notational clarity, we use the following convention (adapted from~\cite{miller2016honey}) throughout this work.
\begin{itemize}
\item Lower case (e.g. $x$) denotes a scalar object or a tuple.
\item Upper case (e.g. $X$) denotes a set or a constant.
\item Sans serif (e.g. $\textsf{fn}(\cdot)$) denotes a function.
\item Monospace (e.g. $\texttt{ack}$) denotes message type.
\end{itemize}
Further, we use $a || b$ to denote concatination of the binary representations of $a$ and $b$.
